Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-21 xrb2/paper.tex
Added streamline plot

{\color{blue}
For some of our analysis, we would like to have a means of estimating the temperature and nuclear 
energy generation rate in the burning region of each simulation. For this purpose, we define 
$\repavg{Q}$ to be the mass weighted average
\begin{equation}
	\label{eqn:top_percentile_avg}
	\repavg{Q} \equiv \frac{\sum_{c_i} m(c_i) Q(c_i)}{\sum_{c_i} m(c_i)}; ~c_i \in C_{99}(Q).
\end{equation}
\noindent Here, $C_{99}(Q)$ is the set of grid cells with $Q$ values in the top percentile, and 
$Q(c_i)$ is the value of the quantity $Q$ in cell $c_i$. An alternative to doing this averaging is 
to simply take the maximum of the quantity across the entire simulation domain, but using 
$\repavg{Q}$ instead allows us to track changes over a region rather than at a single localized 
point. Figure \ref{fig:maxima} shows $\repavg{T}$ and $\repavg{\enucdot}$ as functions of time for 
the subset of our runs that achieve a propagating flame. This figure is referenced at several 
points throughout the subsequent sections.
}

>>>>

{\color{blue}
For some of our analysis, we would like to have a means of estimating the temperature and nuclear 
energy generation rate in the burning region of each simulation. For this purpose, we define 
$\repavg{Q}$ to be the mass weighted average
\begin{equation}
	\label{eqn:top_percentile_avg}
	\repavg{Q} \equiv \frac{\sum_{c_i} m(c_i) Q(c_i)}{\sum_{c_i} m(c_i)}; ~c_i \in C_{99}(Q).
\end{equation}
\noindent Here, $C_{99}(Q)$ is the set of grid cells with $Q$ values in the top percentile, and 
$Q(c_i)$ is the value of the quantity $Q$ in cell $c_i$. An alternative to doing this averaging is 
to simply take the maximum of the quantity across the entire simulation domain, but using 
$\repavg{Q}$ instead allows us to track changes over a region rather than at a single localized 
point. Figure \ref{fig:maxima} shows $\repavg{T}$ and $\repavg{\enucdot}$ as functions of time for 
the subset of our runs that achieve a propagating flame. This figure is referenced throughout the 
subsequent sections.
}

\begin{figure}
	\plotone{streamlines_500Hz_temp.pdf}
	\caption{\label{fig:streamlines}Streamlines showing the velocity field at time $t = 
	100~\mathrm{ms}$ for the {\tt F500} run. Streamline segments are colored by transverse velocity 
	(yellower implies faster flow), and segments with transverse velocity $v < 2 \times 
	10^6~\mathrm{cm/s}$ are scrubbed out. Note that the plot has been stretched vertically to 
	better show the streamlines -- the aspect ratio is not the aspect ratio of the simulation 
	domain.}
\end{figure}

{\color{blue} Figure \ref{fig:streamlines} shows the velocity field. Not sure where we want to put 
this.}
